---
title: "My Webpage"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = F, warning = F}
library(dplyr)
library(tidyr)
library(ggplot2)
library(DT)
library(leaflet)
```

# Prepare Data

+ read in data from KNB link
+ calculate total salmon escapement by region and species in 2010


```{r}
esc <- read.csv("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af119a05b-bbe7-4aea-93c6-85434dcb1c5e", stringsAsFactors = F)

head(esc)
```

```{r}
region_esc <- esc %>% 
  separate(sampleDate, c("year", "month", "day")) %>% # create year column
  filter(year == 2010) %>% 
  group_by(Species, SASAP.Region) %>% 
  summarise(total_escapement = sum(DailyCount)) %>% # calculate annual escapement
  filter(Species %in% c("Chinook", "Sockeye", "Pink", "Coho", "Chum")) 
  

datatable(region_esc)
```


# Static Visualizations

+ Bar plot of escapement by species

```{r}
ggplot(region_esc, aes(x = Species, y = total_escapement)) +
  geom_bar(stat = "identity")
```

+ Bar plot of escapement by species and region

```{r}
ggplot(region_esc, aes(x = Species, y = total_escapement, fill = SASAP.Region)) +
  geom_bar(stat = "identity") +
  ylab("Total Escapement") +
  theme_bw()
```

# Dynamic Visualizations

+ Map the locations of escapement observations

## Data Preparation

+ find unique locations

```{r}
locations <- esc %>% 
  distinct(Location, Latitude, Longitude) %>% 
  drop_na()

datatable(locations)
```


Interactive leaflet map of escapement locations

```{r}
leaflet(locations) %>% 
  addTiles() %>% 
  addMarkers(~Longitude, ~Latitude, popup = ~Location)
```

